What We Eval in the Shadows

### 2021-08-11 paper/main.tex
Better show LHS in Figure 10
match.call -> formals

\begin{figure}[h]
	\centering
	\begin{tikzpicture}[
		every node/.style={draw, rounded corners, fill=LightGray, text width = 2cm, align = center}
		]
		\node (E) at (2,0) {\c{eval(e)}};
		\node[text width = 3cm] (CA) at (2, 1.5) {\c{[[<-(e, 2, quote(c))}};
		\node (Q) at (0, 3) {\c{quote(c)}};
		\node[text width = 4cm] (A) at (4, 3) {\c{e <- parse(text = "a ; b"}};
		\node[text width = 3cm] (P) at (4, 4.5) {\c{parse(text = "a ; b"}};

@@

\paragraph{Discussion}
The main use case for \eval involves using \c{match.call}, \c{substitute}, or
\c{match.call} to access and transform arguments of a function. Constructing
expressions from strings is also a common use case. The constructed category
shows that most \evals comes from existing code that was modified by the
programmer before invoking \eval. Both constructed and reflection categories
roughly correspond to meta-programming. Some use cases could likely be replaced
by macros if the R designers could be convinced to overcome their distaste for
those. Another use of \eval is to directly build symbols to evaluate them in
another environment.

>>>>

\begin{figure}[h]
	\centering
	\begin{tikzpicture}[
		every node/.style={draw, rounded corners, fill=LightGray, text width = 2cm, align = center}
		]
		\node (E) at (2,0) {\c{eval(e)}};
		\node[text width = 3cm] (CA) at (2, 1.5) {\c{[[<-(e, 2, quote(c))}};
		\node (Q) at (4, 3) {\c{quote(c)}};
		\node[text width = 4cm] (A) at (0, 3) {\c{e <- parse(text = "a ; b"}};
		\node[text width = 3cm] (P) at (0, 4.5) {\c{parse(text = "a ; b"}};

@@

\paragraph{Discussion}
The main use case for \eval involves using \c{match.call}, \c{substitute}, or
\c{formals} to access and transform arguments of a function. Constructing
expressions from strings is also a common use case. The constructed category
shows that most \evals comes from existing code that was modified by the
programmer before invoking \eval. Both constructed and reflection categories
roughly correspond to meta-programming. Some use cases could likely be replaced
by macros if the R designers could be convinced to overcome their distaste for
those. Another use of \eval is to directly build symbols to evaluate them in
another environment.
